User-level Grid Monitoring with Inca 2

### 2007-02-26 pubs/papers/hpdc-gmw-2007/paper.tex
fixes to print floats in order
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6560 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3
I put in my first draft
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6562 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

\documentclass[times,10pt,twocolumn]{article} 
\usepackage{epsfig}
\usepackage{latex8}
\usepackage{listings}
\usepackage{subfigure}
\usepackage{times}
\usepackage{url}

@@

\begin{figure*}[htb]
  \centering
  \mbox{\epsfig{file=arch.eps, width=.7\textwidth}}
  \caption{\label{arch_fig} Inca architecture.}
\end{figure*}

@@

\lstset{
  basicstyle=\scriptsize\ttfamily, 
  frame=single,
  keywordstyle=\textbf, 
  identifierstyle=, 
  commentstyle=\scriptsize\ttfamily, 
  stringstyle=\ttfamily, 
  numbers=left, 
  numberstyle=\scriptsize,
  stepnumber=2,
  firstnumber=1,
  showstringspaces=false} 
\begin{figure}
\lstset{language=Perl} 
\subfigure[]{\lstinputlisting{grid.globus.gramPing}}
\lstset{language=XML,keywordstyle={}} 
\subfigure[]{\lstinputlisting{grid.globus.gramPing.out}}
\caption{\label{pingReporter}(a) An Inca reporter that tests the user-level
availability of a Globus GRAM server and (b) an output sample.}
\end{figure}

@@

\begin{figure*}[htb]
  \centering
  \mbox{\epsfig{file=incat.eps, width=\textwidth}}
  \caption{\label{incat_fig} Screenshot of incat that shows the reporters
  and their attributes available from the provided reporter repository.}
\end{figure*}

@@

\begin{figure}[hbt]
  \centering
  \includegraphics[scale=0.6]{tg-deploy.eps}
  \caption{TeraGrid's Inca 2 Deployment.}
  \label{tg_deploy_fig}
\end{figure}

@@

\begin{figure}[hbt]
  \centering
  \includegraphics[scale=0.4]{status-page.eps}
  \caption{Portion of the TeraGrid CTSSv3 detailed status page with the
  resources anonymized.}
  \label{status_page_fig}
\end{figure}

@@

% Describe GrASP probes

@@

% Used to deploy GrASP probes to Grids.  Probes wrapped as reporters (maybe
% right in future as though we already included GrASP as a dependency cause
% it should be done by June.

@@

% A paper.  Interesting that error messages were important.  Predictions?

>>>>

\documentclass[times,10pt,twocolumn]{article} 
\usepackage{dblfloatfix}
\usepackage{epsfig}
\usepackage{latex8}
\usepackage{listings}
\usepackage{subfigure}
\usepackage{times}
\usepackage{url}

@@

\begin{figure*}[tbp]
  \centering
  \mbox{\epsfig{file=arch.eps, width=.7\textwidth}}
  \caption{\label{arch_fig} Inca architecture.}
\end{figure*}

@@

\lstset{
  basicstyle=\scriptsize\ttfamily, 
  frame=single,
  keywordstyle=\textbf, 
  identifierstyle=, 
  commentstyle=\scriptsize\ttfamily, 
  stringstyle=\ttfamily, 
  numbers=left, 
  numberstyle=\scriptsize,
  stepnumber=2,
  firstnumber=1,
  showstringspaces=false} 
\begin{figure}[tbp]
\lstset{language=Perl} 
\subfigure[]{\lstinputlisting{grid.globus.gramPing}}
\lstset{language=XML,keywordstyle={}} 
\subfigure[]{\lstinputlisting{grid.globus.gramPing.out}}
\caption{\label{pingReporter}(a) An Inca reporter that tests the user-level
availability of a Globus GRAM server and (b) an output sample.}
\end{figure}

@@

\begin{figure*}[tbp]
  \centering
  \mbox{\epsfig{file=incat.eps, width=\textwidth}}
  \caption{\label{incat_fig} Screenshot of incat that shows the reporters
  and their attributes available from the provided reporter repository.}
\end{figure*}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[scale=0.6]{tg-deploy.eps}
  \caption{TeraGrid's Inca 2 Deployment.}
  \label{tg_deploy_fig}
\end{figure}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[scale=0.4]{status-page.eps}
  \caption{Portion of the TeraGrid CTSSv3 detailed status page with the
  resources anonymized.}
  \label{status_page_fig}
\end{figure}

@@

% Describe GrASP probes
The Grid Assessment Probes (GrASP)~\cite{grasp} are designed to 
serve as simple grid application kernel exemplars as well as a 
set of diagnostic tools. They test and measure performance of 
basic grid functions including file transfers, remote execution, 
and Grid Information Services response.  There are two basic probes: i.  The
circle probe takes a 100 MB file and passes it in a ring through a given set
of grid nodes, measuring transfer time at each step.  ii.  The gather probe
transfers a 100 MB file from some number of source nodes to a compute node,
runs a computation through the job queue on the compute resource and then
transfers a 100 MB file to a single destination node.  The transfer of the
first set of files is executed in parallel.  Once again all tranfers times, as
well as compute and queue times are recorded.

The GrASP probes yield useful data on the performance and reliability of the
grid infrastructure that they are run on, but in order to gather a large
amount of data over time we found it necessary to run them on a schedule and
gather any error messages that took place during the execution.  In order to
fulfill the last 2 requirements we deployed the GrASP probes as reporters
within the Inca framework.

@@

The GrASP probes have been written to follow the specifications of an Inca
reporter.  Porting the original code to follow the specifications proved to be
trivial.  Inca was also used to store all of the GrASP data and related error
messages.

@@

Using Inca GrASP was deployed on TeraGrid and Geon for a period of over 6
months.  The data gathered during that period yielded a paper, Measuring the
Performance and Reliability of Production Computational Grids ~\cite{grasp2}.
Through the running of the GrASP probes over such an extended period of time
we were able to identify a recurring Globus 2 bug and were able to predict the
execution time of Preco, a Grid application run on the TeraGrid within 12\%
excluding setup and cleanup time.
